On the adhesivity of EGGS

### 2025-02-13 calco/main.tex
Update main.tex

\title{On the adhesivity properties of equivalence graphs\thanks{???????}}

@@

\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}

\begin{document}

\tikzset{->-/.style={decoration={
			markings,
			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
	\maketitle \todo{Scegliere un titolo vero e mettere i ringraziamenti}
	\begin{abstract}
\todo{a very nice abstract}
	\end{abstract}

@@

This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.

@@

\subsection{$\mathcal{M}$-adhesivity}\label{subsec:ade}
The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.

@@

\subsection{Kernel Pairs and Regular Epimorphisms}

>>>>

%\tikzset{->-/.style={decoration={
%			markings,
%			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}

@@

\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
\Copyright{R.~Biondo, D.~Castelnovo, F.~Gadducci}

\ccsdesc[500]{Theory of Computation~Models of computation}
\ccsdesc[500]{Theory of Computation~Semantics and reasoning}

\keywords{Adhesive categories, EGGS} %TODO mandatory; please add comma-separated list of keywords

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}

\title{On the adhesivity of EGGS}

\begin{document}
\maketitle

\begin{abstract}
\todo{a very nice abstract}
\end{abstract}

@@

This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}
and investigate some simple results for their relationship with kernel pairs.

@@

\subsection{Background on $\mathcal{M}$-adhesivity}\label{subsec:ade}
The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.

@@

\subsection{Some Results on Kernel Pairs and Regular Epis}
